Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-28 paper/current/main.tex

The \SGNS{} model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
Similarly, embedding distance outperforms personalized-page rank distance ($R^{2} = XYZ$, Fig. SI~\ref{fig:supp:gravity_ppr}a), a network-based measure. 
Embedding distance also explains more of the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig. ~\ref{fig:supp:gravity_correlation}d) than does geographic distance. 
After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.

>>>>

The \SGNS{} model learns an effective distance that explains and predicts scientific mobility better than alternatives. 
Embedding distance explains more of the expected flow between pairs of organizations, with correlation ($R^{2} = 0.46$, Fig.~\ref{fig:gravity_performance}a) over double that of geographic distance ($R^{2} = 0.22$, Fig.~\ref{fig:gravity_performance}b).
Embedding distance also explains more of the variance of domestic (Fig.~\ref{fig:supp:gravity_correlation}c) and international mobility flows (Fig. ~\ref{fig:supp:gravity_correlation}d) than does geographic distance. 
After fitting model parameters from the data, the embedding distance produces better predictions of expected flux than does geographic distance globally (Fig.~\ref{fig:gravity_performance}c-d) and for domestic (Fig.~\ref{fig:supp:gravity_correlation}e-f) and international mobility(Fig.~\ref{fig:supp:gravity_correlation}g-h).
Similarly, embedding distance outperforms distances derived from calculating personalized-page rank scores on the underlying mobility network (Fig.~\ref{fig:supp:gravity_pprcos}, Fig.~\ref{fig:supp:gravity_pprjsd}). 
Geographic distance alone is a poor tool for understanding international scientific mobility---rather, by learning a distance directly from the data, it is possible to better explain, and better predict flux between organizations.
